\documentclass[12pt, titlepage]{article}

\usepackage{xcolor} % for different colour comments
\usepackage{tabto}
\usepackage{mdframed}
\usepackage{xkeyval}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[singlelinecheck=off, skip=2pt, labelfont=bf]{caption}

%% Comments
\newif\ifcomments\commentstrue

\ifcomments
\newcommand{\authornote}[3]{\textcolor{#1}{[#3 ---#2]}}
\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
\else
\newcommand{\authornote}[3]{}
\newcommand{\todo}[1]{}
\fi

\newcommand{\wss}[1]{\authornote{magenta}{SS}{#1}}
\newcommand{\ds}[1]{\authornote{blue}{DS}{#1}}

\makeatletter

\define@cmdkey      [SRS] {req}     {use}     {}
\define@cmdkey      [SRS] {req}     {desc}      {}
\define@cmdkey      [SRS] {req}     {rationale} {}
\define@cmdkey      [SRS] {req}     {orig}      {}
\define@cmdkey      [SRS] {req}     {fit}       {}
\define@cmdkey      [SRS] {req}     {sat}       {}
\define@cmdkey      [SRS] {req}     {dissat}    {}
\define@cmdkey      [SRS] {req}     {priority}  {}
\define@cmdkey      [SRS] {req}     {conf}      {}
\define@cmdkey      [SRS] {req}     {supp}      {}
\define@cmdkey      [SRS] {req}     {hist}      {}


\newcounter{ReqNum}
\newcommand{\req}[1]{
\setkeys[SRS]{req}{#1}
\stepcounter{ReqNum}
\begin{mdframed}
\noindent {\bf Requirement \#:} \arabic{ReqNum} \tabto{4.6cm} {\bf Requirement Type:} \arabic{section}.\arabic{subsection} \tabto{10.2cm} {\bf Use Case:} \cmdSRS@req@use\\[\baselineskip]
\begin{tabularx}{\textwidth}{@{}p{3cm}X@{}}
{\bf Description:} & \cmdSRS@req@desc\\
{\bf Rationale:} & \cmdSRS@req@rationale\\
{\bf Originator:} & \cmdSRS@req@orig\\
{\bf Fit Criterion:} & \cmdSRS@req@fit\\[\baselineskip]
\end{tabularx}
\begin{tabularx}{0.5\textwidth}{@{}p{4cm}X@{}}
{\bf Cust. Satisfaction:} & \cmdSRS@req@sat \\
{\bf Priority:} & \cmdSRS@req@priority \\[\baselineskip]
\end{tabularx}
\begin{tabularx}{0.5\textwidth}{@{}p{4.5cm}X@{}}
{\bf Cust. Dissatisfaction:} & \cmdSRS@req@dissat\\
{\bf Conflicts:} & \cmdSRS@req@conf\\[\baselineskip]
\end{tabularx}
\begin{tabularx}{\textwidth}{@{}p{5cm}X@{}}
{\bf Supporting Materials:} & \cmdSRS@req@supp\\
{\bf History:} & \cmdSRS@req@hist
\end{tabularx}
\end{mdframed}}

\makeatother


\begin{document}

\title{\bf Physics-Based Chipmunk2D Game\\[\baselineskip]\Large Software Requirements Specification}
\author{Steven Palmer\\Emaad Fazal\\Chao Ye}
\date{\today}
	
\maketitle

\pagenumbering{roman}
\tableofcontents
\listoftables

\begin{table}[bp]
\caption*{\bf Revision History}
\begin{tabularx}{\textwidth}{p{3cm}p{3cm}p{2cm}X}
\toprule {\bf Author} & {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
Steven Palmer & October 7, 2015 & 1.0 & Created document\\ 
\bottomrule
\end{tabularx}
\end{table}

\newpage
\pagenumbering{arabic}
\section{Project Drivers}
\subsection{The Purpose of the Project}
The purpose of this project is to produce a game that will be used as a demonstration for students in a third year software engineering game design course at McMaster University.  The game will incorporate the \href{https://chipmunk-physics.net/}{Chipmunk2D} physics library and highlight its capabilities.
\subsection{The Stakeholders}
\subsubsection{The Client}
The client for this project is \href{http://www.cas.mcmaster.ca/~smiths/}{Dr. Spencer Smith} of the Computing and Software department at McMaster University.
\subsubsection{The Customer}
The customer for this project are students who will take the game design course in the future.
\subsubsection{Other Stakeholders}
Other stakeholders include future instructors of the game design course and other related courses.
\section{Project Constraints}
\subsection{Mandated Constraints}

\subsection{Naming Conventions and Terminology}
The terminology used in this project is given in \hyperref[tab:terminology]{Table~\ref*{tab:terminology}}.
\begin{table}
\caption{List of terminology} \label{tab:terminology}
\begin{tabularx}{\textwidth}{p{3cm}X}
\toprule {\bf Term} & {\bf Definition}\\
\midrule
Boss & Important enemy with increased stats\\
Bounds & The boundaries inside which game play occurs\\
Character & A\\
Enemy & Hostile NPC; normally attacks hero\\
Hero & The main character of the game controlled by the user\\
NPC & Non-playable character; may be friendly or hostile\\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Relevant Facts and Assumptions}

\section{Functional Requirements}
\subsection{The Scope of the Work}
\subsection{Business Data Model and Data Dictionary}
\subsection{The Scope of the Product}
\subsection{Functional Requirements}

\req{
        use = 1,
        desc = The \hyperref[tab:terminology]{hero} shall remain in \hyperref[tab:terminology]{bounds},
        rationale = The \hyperref[tab:terminology]{hero} must remain in the intended boundaries of play for the game to function properly,
        orig = Steven Palmer,
        fit = \hyperref[tab:terminology]{Hero} is unable to pass through walls and other obstacles,
        sat = 5,
        dissat = 5,
        priority = High,
        conf = None,
        supp = None,
        hist = {Created October 7, 2015}
}

\section{Non-functional Requirements}
\subsection{Look and Feel Requirements}
\subsection{Usability and Humanity Requirements}
\req{
        use = 1,
        desc = The game shall be entertaining,
        rationale = A game that is not fun is a failure,
        orig = Steven,
        fit = The game should be ranked at least 7/10 for entertainment based on a usability study,
        sat = 2,
        dissat = 5,
        priority = High,
        conf = None,
        supp = None,
        hist = {Created October 7, 2015}
}
\subsection{Performance Requirements}
\req{
        use = 1,
        desc = The game shall maintain a framerate of at least 30 fps,
        rationale = A framerate of 30 fps or greater will ensure smooth animation,
        orig = Steven,
        fit = The game shall ,
        sat = 2,
        dissat = 5,
        priority = High,
        conf = None,
        supp = None,
        hist = {Created October 7, 2015}
}
\subsection{Operational and Environmental Requirements}
\subsection{Maintainability and Support Requirements}
\req{
        use = 1,
        desc = {The game shall support Windows, Linux, and OS X operating systems},
        rationale = Students use a variety of operating systems,
        orig = Spencer Smith,
        fit = Check that game compiles and runs on each operating system,
        sat = 3,
        dissat = 3,
        priority = High,
        conf = None,
        supp = None,
        hist = {Created October 7, 2015}
}
\subsection{Security Requirements}
There are no security requirements related to this project.
\subsection{Cultural Requirements}
\req{
        use = 1,
        desc = {The game shall use the English language},
        rationale = Students at McMaster University are expected to speak English,
        orig = Steven,
        fit = The game will use proper English free of spelling and grammar errors,
        sat = 1,
        dissat = 3,
        priority = Medium,
        conf = None,
        supp = None,
        hist = {Created October 7, 2015}
}
\subsection{Legal Requirements}
There are no legal requirements related to this project.

\section{Project Issues}
\subsection{Open Issues}
There are no open issues at this time.  This section will be updated as required.
\subsection{Off-the-Shelf Solutions}
There are no off-the-shelf solutions.
\subsection{New Problems}
No new problems are expected to arise as a result of this project.
\subsection{Tasks}

\subsection{Migration to the New Product}
There is no product being replaced, and thus no migration is required.
\subsection{Risks}
There are no risks associated with this project.
\subsection{Costs}
There are no costs associated with this project.
\subsection{User Documentation and Training}
User documentation will be created with .  Training will be provided via built-in tutorials throughout the game.
\subsection{Waiting Room}
At this point in the project timeline, there are no backlogged requirements.  This section will be updated as required.
\subsection{Ideas for Solutions}
There are no ideas for solutions at this time.  This section will be updated as required.
\end{document} 